### 2024-11-27 bugs.qmd
20241126 - calculate_stats() function from nflfastR, TODOs, and bugs

Bugs to report (`nflreadr`):

- `players` database has a season column but it is only populated for some players, and it is only populated with 2020
- `player_stats` database of weekly stats does not have a `game_id` column

>>>>

Bugs to report (`nflreadr` or `nflfastR`):

- `players` database has a season column but it is only populated for some players, and it is only populated with 2020 (<https://github.com/nflverse/nflreadr/issues/238>)
- `player_stats` database of weekly stats does not have a `game_id` column (<https://github.com/nflverse/nflreadr/issues/238>)
- common naming convention for key variables, for purposes of merging (<https://github.com/nflverse/nflreadr/issues/237>)
- use of deprecated `summarise()` for returning more than 1 row per group; use `reframe()` instead (<https://github.com/nflverse/nflfastR/issues/480>)
- calculate career stats using `calculate_stats()` function

### 2024-11-27 download-football-data.qmd
20241126 - calculate_stats() function from nflfastR, TODOs, and bugs

@@

@@

>>>>

First, we can compute the players' career statistics using the `calculate_stats()` function from the `nflfastR` package.

TODO: Insert code example.

##### OLD (DELETE CODE BELOW)

@@

TODO: Save/update data file in repo with the data generated from this code, and follow the data file through the rest of the book, updating code as necessary.

```{r}
#| eval: false
nfl_actualStats_seasonal_player_raw <- calculate_stats(
  seasons = TRUE,
  summary_level = "season",
  season_type = "REG")

nfl_actualStats_seasonal_team_raw <- calculate_stats(
  seasons = TRUE,
  summary_level = "season",
  stat_type = "team",
  season_type = "REG")
```

save(
  nfl_actualStats_seasonal_player_raw, nfl_actualStats_seasonal_team_raw,
  file = "./data/nfl_actualStats_seasonal_raw.RData"
)
```

The `nfl_actualStats_seasonal_player_raw` object is in `player`-`season` form.
That is, each row should be uniquely identified by the combination of `player_id` and `season`.
The `nfl_actualStats_seasonal_team_raw` object is in `team`-`season` form.
That is, each row should be uniquely identified by the combination of `team` and `season`.
Let's rearrange the data accordingly:

```{r}
nfl_actualStats_seasonal_player <- nfl_actualStats_seasonal_player_raw %>% 
  rename(team = recent_team) %>% 
  select(player_id, season, everything()) %>% 
  arrange(player_display_name, player_id, season)

nfl_actualStats_seasonal_team <- nfl_actualStats_seasonal_team_raw %>% 
  select(season, team, everything()) %>% 
  arrange(season, team)
load(file = "./data/nfl_actualStats_seasonal.RData")
```

##### OLD (DELETE CODE BELOW)

@@

TODO:

- Decide whether to use `calculate_stats()` from `nflfastR` or `load_player_stats()` from `nflreadr`.
- Save/update data file in repo with the data generated from the relevant code, and follow the data file through the rest of the book, updating code as necessary.

```{r}
#| eval: false
nfl_actualStats_weekly_raw <- calculate_stats(
  seasons = TRUE,
  summary_level = "week")

nfl_actualStats_weekly_defense_raw <- calculate_stats(
  seasons = TRUE,
  summary_level = "week",
  stat_type = "team")
```

##### OLD (DELETE CODE BELOW)
